Working Script

### 2020-09-29 WorkingScript.Rmd
Loaded in new datasets

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedSep1.csv")
```

@@

```{r}
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanAug29.csv", header = T)
```

@@

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  geom_point(aes(color = food))
```

@@

@@

>>>>

```{r}
data <- read.csv("~/Desktop/MsCcHSFeedSep15modfinal.csv")
```

@@

```{r}
scan <- read.csv("~/Desktop/MsCcHSFeedLeafScanFinal.csv", header = T)
```

@@

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  geom_point(aes(color = food)) + 
  labs(x = "Maximum mass achieved (mg)", y = "Leaf surface area consumed (cm2)", color = "Food type")
```

```{r}
ggplot(data, aes(x = mass.max, y = area)) + 
  geom_point(aes(color = fate))
```

@@

```{r}
mod1.5 <- lm(area ~ mass.max + food, data = data)

summary(mod1.5)
```

```{r}
mod1.75 <- lm(area ~ mass.max + food*para, data = data)

summary(mod1.75)
```

@@

## Adding in random effect of bin

```{r}
mod4 <- lmer(area ~ mass.max + (1|bin), data = data)

summary(mod4)
```

It's a singluar fit - I could switch all of my individual bins to the same number? Would that work?

Let's check the effect of group vs. individual bins

```{r}
mod5 <- lmer(area ~ mass.max + (1|bin.type), data = data)

summary(mod5)
```

```{r}
mod6 <- lmer(mass.max ~ food*para*HS + (1|bin), data = data)

summary(mod6)
```

```{r}
mod6.5 <- lmer(mass.max ~ food + para + HS + (1|bin), data = data)

summary(mod6.5)
```

The above model is the only one that isn't singular!!

```{r}
mod7 <- lmer(mass.max ~ food*para*HS + (1|bin.type), data = data)

summary(mod7)
```

```{r}
mod8 <- lmer(mass.max ~ para*HS + (1|bin), data = data)

summary(mod8)
```

Let's test some models with AIC

```{r}
AIC(mod1, mod1.5, mod1.75, mod3, mod4, mod5)
```

Model 1 and model 1.75 are indistinguishable - so you need food and para and their interaction to get the full picture for area

```{r}
AIC(mod2,mod6, mod6.5, mod7, mod8)
```

Mods 6 and 7 are indistinguishable - you need the random effect of bin, but bin and bin type have the same effect? You also need all the interactive terms, even though they aren't significant.

```{r}
data2 <- read.csv("~/Desktop/MsCcHSFeedSep15binmod2.csv")
```

```{r}
consumedsum2 <- consumedsum[consumedsum$ID %in% data2$ID, ]

data2 <- data2[data2$ID %in% consumedsum2$ID, ]

consumedsum2 <- consumedsum2[order(consumedsum2$ID), ]

data2$area <- consumedsum2$totalarea
```

Let's try it now

```{r}
modcomb <- lmer(area ~ mass.max + (1|bin), data = data2)

summary(modcomb)
```
